\documentclass[draftclsnofoot,onecolumn]{IEEEtran}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}         


\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}


\geometry{textheight=8.5in, textwidth=6in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\usepackage{longtable}


\newcommand{\longtableendfoot}{Please continue at the next page}

\def\name{Andrew Chase}

\date{}
\author{\name \\ 
OS II \\
Spring 2015 \\
Abstract: Describes work done to build and run a custom Memory Allocator.
}
\title{Project 4: The SLOB SLAB}

%pull in the necessary preamble matter for pygments output
\input{pygments.tex}


\begin{document}

\maketitle

\pagebreak

\tableofcontents

\pagebreak

\section{Work Log}

\begin{tabular}{ll}
  \textbf{Date} & \textbf{Work Done} \\
  June 3 & Did research, modified slob.c, wrote frag.py
\end{tabular}

\section{Questions}

\subsection{What do you think the main point of this assignment is?}

I think the main point of the assignment is to learn about memory management in operating systems and how the Linux memory management system works.

\subsection{How did you personally approach the problem? Design decisions, algorithm, etc.}

As usual first I looked up other approaches to the problem. Next I designed a simple algorithm. I focused on trying to make as few changes to the slob.c module as possible. My algorithm is a little wasteful as it goes through the whole list of blocks twice, once to find the best fit, and once to re-find the best-fit block to select it for use.

For the memory fragmentation I found a reference for a linux system tool that allows me to grab the list of blocks easily so that I can perform operations on them.

\subsection{How did you ensure your solution was correct? Testing details, for instance.}

I ensured my solution was correct by reading the /proc/buddyinfo file which reveals the free memory blocks and their sizes. I also inserted printk messages to example the values of the variables at one point when my solution wasn't working correctly.

\subsection{What did you learn?}

I learned a bit about how the Linux block allocator works and how the different algorithms can effect performance. I also learned a bit about how to debug memory errors in QEMU. I learned how to perform research and wire up solutions to problems in Kernel development.

\section{Git Log}

\begin{tabular}{lp{12cm}}
  \label{tabular:legend:git-log}
  \textbf{acronym} & \textbf{meaning} \\
  V & \texttt{version} \\
  tag & \texttt{git tag} \\
  MF & Number of \texttt{modified files}. \\
  AL & Number of \texttt{added lines}. \\
  DL & Number of \texttt{deleted lines}. \\
\end{tabular}

\bigskip

\iflanguage{ngerman}{\shorthandoff{"}}{}
\begin{longtable}{|rlllrrr|}
\hline \multicolumn{1}{|c}{\textbf{V}} & \multicolumn{1}{c}{\textbf{tag}}
& \multicolumn{1}{c}{\textbf{date}}
& \multicolumn{1}{c}{\textbf{commit message}} & \multicolumn{1}{c}{\textbf{MF}}
& \multicolumn{1}{c}{\textbf{AL}} & \multicolumn{1}{c|}{\textbf{DL}} \\ \hline
\endhead

\hline \multicolumn{7}{|r|}{\longtableendfoot} \\ \hline
\endfoot

\hline% \hline
\endlastfoot

\hline 1 &  & 2014-12-09 & Merge tag 'v3.14.24' & 45949 & 18281318 & 0 \\
\hline 2 &  & 2016-06-03 & Add plan & 1 & 14 & 0 \\
\hline 3 &  & 2016-06-03 & Implement best-first & 1 & 27 & 30 \\
\hline 4 &  & 2016-06-03 & Fix int declarations to c90 & 1 & 5 & 4 \\
\hline 5 &  & 2016-06-03 & Fix additional warnings & 1 & 7 & 5 \\
\hline 6 &  & 2016-06-03 & Fix bug where slob would never allocate & 1 & 3 & 3 \\
\hline 7 &  & 2016-06-03 & Fix reversed for loop args & 1 & 1 & 1 \\
\hline 8 &  & 2016-06-03 & Fix base case & 1 & 1 & 1 \\
\hline 9 &  & 2016-06-03 & Fix no memory available & 1 & 4 & 2 \\
\hline 10 &  & 2016-06-03 & Fix memory freeze & 1 & 5 & 2 \\
\hline 11 &  & 2016-06-03 & Add fragmentation percentage script & 1 & 32 & 0 \\
\end{longtable}


\section{Code Listing}

\subsection{slob.c}

\input{slob.c.tex}

\subsection{frag.py}

\input{frag.py.tex}

\end{document}
